---
title: "hw5"
author: "sze pui"
date: "11/20/2021"
output: github_document
---

```{r load library}
library("tidyverse")
library("purrr")
library("readxl")
```


#Problem 1 

```{r}
#drop the cells with unknown or blank
homicide_df = read_csv("homicide_data.csv", na = c("","Unknown"))
 homicide_df = homicide_df %>%
   mutate(      #combind city and state together for easy reading 
     city_state = str_c(city, state),
      resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved")) %>% 
   relocate(city_state)%>% 
  filter(city_state != "TulsaAL")
```
Lets focus on baltimore first...
```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "BaltimoreMD") 
baltimore_summary = 
baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"), 
    n = n()
  )
baltimore_test = 
prop.test(
  x = baltimore_summary %>% pull(unsolved),
  n = baltimore_summary %>% pull(n)
)
baltimore_test %>% 
  broom::tidy()
```

We will iterate across cities.  write a function first..... 

```{r}
prop_test_function = function(city_df){
city_summary = 
city_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"), 
    n = n()
  )
city_test = 
prop.test(
  x = city_summary %>% pull(unsolved),
  n = city_summary %>% pull(n)
)
return(city_test)
}

#let's test if we can use the function..
homicide_df %>% 
  filter(city_state == "AlbuquerqueNM")%>% 
  prop_test_function()
```

Now, let's iterate across all cities.

```{r}
results_df = 
  homicide_df %>% 
  #nest everything except of city_state 
  nest(data = uid:resolution) %>% 
  mutate(test_results = map(data, prop_test_function), 
         tidy_results = map(test_results, broom::tidy)
         ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>%
  select(city_state, estimate, starts_with("conf"))
```

Make a plot showing estimates and confidence intervals. 

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

#Problem 2 
Data for each participant is included in a separate file, and file names include the subject ID and arm.
Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time


```{r}
files = list.files("./data")

#Start with a dataframe containing all file names
#list.files function lists all the name of the file 
df_with_names = tibble (
  files = list.files("./data"))
```

Iterate over file names and read in data for each subject 
```{r}
df_with_names  = df_with_names %>% 
  #use mutate to keep the original data and save it as a new variable
   mutate(all_file =map(.x = str_c("./data/", files),~read_csv(.x)))%>%
#we have to unnest them since it is nested in the all_file column
  unnest(cols = all_file)
```

Lets tidy the data.
```{r}
tidy_data = df_with_names %>% 
   separate(files, into = c("file_type", "number"), sep = "_") %>% 
  #remove a specific word from a column using str_remove_all
   mutate(number = str_remove_all(number,".csv"),
          #example: fct_recode(x, fruit = "apple", fruit = "banana")
         file_type = recode(file_type ,con = "control", exp= "experimental") )

  
```





#Problem 3
```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```
There are two cases to address:

(1)numeric variables: fill in missing values with the mean of non-missing values
(2) character variables:fill in missing values with "virginica"

Write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector. 

Let's try to write a function first to replace the missing value...
```{r}
#refer to the example of mean_and_sd in lecture
missing_value = function(vector){
  if(is.character(vector)){
    # tidyr::replace_na(), which replaces an NA value with a specified value
    vector = replace_na(vector, "virginica")
    return(vector)}
  else if(is.numeric(vector)){
    vector = replace_na(vector, mean(vector, na.rm = TRUE))
  }
}
```
lets try to map the function and save it in a new dataframe 

```{r}
map(iris_with_missing,missing_value) 
#map variants, ref to Iteration and List Columns
output = map_dfr(iris_with_missing,missing_value, .id = "input")

```

